---
title: 'Day-5: 15 Oct, 18'
author: "tiangsinf"
date: "15/13/2018"
output: 
  html_document:
    keep_md: yes
---
## GLM: Logistic Regression

```{r, clear workspace, echo = FALSE, eval = FALSE}
rm(list = ls()) # clear workspace
```

```{r, load packages, message = FALSE}
library(tidyverse)
library(ggvis)
library(grid)
library(gridExtra)
library(pROC)
data("Default", package = "ISLR")
```

```{r}
default <- Default %>%
  mutate(default = as.numeric(ifelse(
    default == "No", 0, 1)))
  
default <- default %>%
  mutate(student = ifelse(
    student == "No", 0, 1))
```

```{r}
ggvis(x = ~balance, fill = ~default, default) %>%
  group_by(default) %>%
  layer_densities(stroke := "white")
# people that have higer balance tend to default

ggvis(x = ~income, fill = ~default, default) %>%
  group_by(default) %>%
  layer_densities(stroke := "white")
# income is pretty close between the default and non-default group. Might not be particularly useful.
```

```{r}
# model and test data split
sample_index <- sample(nrow(default), round(0.85 * nrow(default), 0))
train <- default[sample_index, ]
test <- default[-sample_index, ]
```

```{r}
x <- names(default[-c(1, 4)])
formula <- as.formula(
  paste(
    "default ~",
    paste(
      x, collapse = " + "
    )
  )
)
```

```{r}
glm_model <- glm(formula = formula, family = binomial(link = logit), data = train)
summary(glm_model)
```
`family = binomial(link = logit)` is used for boolean response variable
`family = gaussian(link = identity)` is used for linear model. Equivalent to `lm()`
`family = poisson(link = log)` is used to counting respond varialbe.
There are other types of `family` as documented in https://www.rdocumentation.org/packages/stats/versions/3.5.1/topics/family

The logistic regression diagnostic values generated by the `summary()` call are typically not used directly to interpret the “goodness of fit” of a model.

### Using the logistic model (predicting on training set)
```{r}
glm_pred <- predict(glm_model, type = "response")

# if probability is > 0.5 than mutate the value to 1 else, 0
glm_pred <- if_else(glm_pred > 0.5, 1, 0)

head(glm_pred)
table(glm_pred)
```
`type` argument is the type of prediction required. The default ("`link`") is on the scale of the linear predictors; the alternative "`response`" is on the scale of the response variable. Thus **for a default binomial model the default predictions are of log-odds (probabilities on logit scale) and `type` = "`response`" gives the predicted probabilities**. The "`terms`" option returns a matrix giving the fitted values of each term in the model formula on the linear predictor scale. 

### Convert probability into binary factor
To use `confusionMatrix`, the response variable for the training and testing set have to be a factor. The following chunck convert the default column from `num` to `factor.`
```{r}
train_fac <- train %>%
  mutate(default = as.factor(default))

test_fac <- test %>%
  mutate(default = as.factor(default))

glm_pred_fac <- as.factor(glm_pred)
```

```{r}
# Model fit on training data
caret::confusionMatrix(glm_pred_fac, train_fac$default) #95.28%
```

### Prediction on test data set
```{r}
glm_predict.test <- predict(glm_model, newdata = test, type = "response")
glm_predict.test <- if_else(glm_predict.test > 0.5, 1, 0)

glm_predict.test_fac <- as.factor(glm_predict.test)
caret::confusionMatrix(glm_predict.test_fac, test_fac$default) #97.33
```

```{r}
roc(test$default ~ glm_predict.test, plot = TRUE, print.auc = TRUE)
```

